\pkg{mlr3spatiotempcv}: Spatiotemporal Resampling Methods for \pkg{mlr3}

### 2021-04-10 paper/paper.Rmd
expand and rotate methods table

  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simplified and generic interface.
  The latter is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine learning framework.
  This simplifies the step of integrating package specific syntax into an overarching machine learning pipeline.
  The hope is that the availability of such a package encourages researchers to more often apply spatiotemporal resampling methods in scientific case studies.
keywords:
  # at least one keyword must be supplied
  formatted: [resampling, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [resampling, machine learning, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{booktabs}
  \usepackage{longtable}
tables: true
bibliography: paper.bib
# output: rticles::jss_article
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---

@@

\begin{table}[h]
	\centering
	\caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column).}
	\begingroup
	\begin{tabular}{llll}
		\\
		Literature                  & Package          & Reference          & Notation                    \\
		\toprule
    Spatial Buffering           & \pkg{blockCV}    & \citet{blockCV}    & \texttt{rsmp("spcv\_buffer")} \\
    Spatial Blocking            & \pkg{blockCV}    & \citet{blockCV}    & \texttt{rsmp("spcv\_block")}  \\
    Spatial CV                  & \pkg{sperrorest} & \citet{sperrorest} & \texttt{rsmp("spcv\_cv")}     \\
    Environmental Blocking      & \pkg{blockCV}    & \citet{blockCV}    & \texttt{rsmp("spcv\_env")}    \\
    \midrule
    Leave-Location-and-Time-Out & \pkg{CAST}       & \citet{cast}       & \texttt{rsmp("spcv\_cstf")}   \\
    Spatiotemporal Clustering   & \pkg{skmeans}    & \citet{cluto}      & \texttt{rsmp("spcv\_cluto")}
	\end{tabular}
	\endgroup\label{tab:sptcv-methods}
\end{table}

>>>>

  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simplified and generic interface.
  The latter is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine learning framework.
  This simplifies the step of integrating package specific syntax into an overarching machine learning pipeline.
  The hope is that the availability of such a package encourages researchers to more often apply spatiotemporal resampling methods in scientific case studies.
keywords:
  # at least one keyword must be supplied
  formatted: [resampling, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [resampling, machine learning, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---

@@

\begin{table}[h]
  \centering
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). }
  \begingroup
  \begin{adjustbox}{angle=270}
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Literature \\
      \toprule
      \multirow{3}{*}{Spatial}        & Spatial Buffering           & \pkg{blockCV}, \pkg{sperrorest}    & "spcv\_buffer", "spcv\_disc()", "spcv\_loo()" & Lit1       \\
                                      & Spatial Blocking            & \pkg{blockCV}, \pkg{sperrorest}  & "spcv\_block",
                                      "spcv\_tiles()"  & Lit1       \\
                                      & Spatial Clustering          & \pkg{sperrorest} & "spcv\_coords" & Lit1       \\
       & Leave-Location-Out & \pkg{CAST}, \pkg{sperrorest}       & "sptcv\_cstf('space\_var')", "spcv\_factor"  & Lit1       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       & "sptcv\_cstf"  & Lit1       \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    & "sptcv\_cluto" & Lit1       \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    & "spcv\_env"    & Lit1       \\
    \end{tabular}
  \end{adjustbox}
  \endgroup\label{tab:sptcv-methods}
\end{table}
